Parallel Global Optimization for Non-Convex Mixed-Integer Problems

### 2019-10-01 2019/RSD_Integer/RSD2019.tex
RSD: add middots and letter symbol
Final
Add one reference for SuperFRI (Sulimov)

\documentclass{llncs}

@@

@@

\title{Parallel Global Optimization for Non-Convex Mixed-Integer Problems
%\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
\author{Konstantin Barkalov \and Ilya Lebedev %\Letter 
\\
\email{ \{konstantin.barkalov,ilya.lebedev\}@itmm.unn.ru}}

@@

\keywords { Global optimization, Non-convex constraints, Mixed-integer problems}

@@

In this paper the global optimization problems and the method of their solving are 
considered. The global optimization problems are the time-consuming ones since the global 
optimum is an integral characteristic of the problem being solved and requires the investigation 
of the whole search domain. 
As a result, the search of the global optimum is reduced to the construction of a coverage (in 
general, a nonuniform one) of the space of parameters. 
The problems, in which some parameters can take the discrete or integer values only (\textit{mixed-integer global 
optimization problems}) are of special interest because for these problems it is more difficult to build 
the estimates of the optimum as compared to the continuous ones.

@@

\begin{figure}
\begin{minipage}{0.49\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1b.JPG} \\ (a)}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1c.JPG} \\ (b)}
\end{minipage}
\caption{Evolvents in two dimensions with (a) $m=4$ and (b) $m=5$}
\label{evolvents}
\end{figure}

@@

>>>>

\documentclass[runningheads]{llncs}

@@

\def\middot{\textperiodcentered~}

@@

\title{Parallel Global Optimization for Non-Convex Mixed-Integer Problems
%\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
\author{Konstantin Barkalov (\Letter) \and Ilya Lebedev %\Letter
\\
\email{ \{konstantin.barkalov,ilya.lebedev\}@itmm.unn.ru}}

@@

\keywords { Global optimization \middot Non-convex constraints \middot Mixed-integer problems
\middot Parallel algorithms}

@@

In this paper the global optimization problems and the method of their solving are
considered. The global optimization problems are the time-consuming ones since the global
optimum is an integral characteristic of the problem being solved and requires the investigation
of the whole search domain.
As a result, the search of the global optimum is reduced to the construction of a coverage (in
general, a nonuniform one) of the space of parameters. 
Such problems are common in applications \cite{Sulimov}.
The problems, in which some parameters can take the discrete or integer values only (\textit{mixed-integer global
optimization problems}) are of special interest because for these problems it is more difficult to build
the estimates of the optimum as compared to the continuous ones.

@@

\begin{figure}
\begin{minipage}{0.49\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1b.jpg} \\ (a)}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1c.jpg} \\ (b)}
\end{minipage}
\caption{Evolvents in two dimensions with (a) $m=4$ and (b) $m=5$}
\label{evolvents}
\end{figure}

@@

\bibitem{Sulimov}
Kutov, D.C., Sulimov, A.V., Sulimov, V.B.: Supercomputer docking: investigation of low energy minima of protein-ligand complexes. Supercomputing Frontiers and Innovations \textbf{5}(3), 134--137 (2018)
